\thesistitle

### 2019-05-07 sattose/paper.tex
Working a bit on stuff

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Therefore, we propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

>>>>

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Therefore, we propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
  \item \textbf{Compare the equality of the fully qualified indentifier for method references and call signatures.}
\end{itemize}

### 2019-05-07 sections/research.tex
Working a bit on stuff

\section{Clone detection survey}
At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. We have considered a set of these tools, including some additional (more recent) ones. However, most of these tools have a vastly different purpose than this thesis. Most of the tools are focused on efficiency and detecting all of the types of clones. Efficiency is lesser of a concern to us, correctness is the most important aspect.

\subsection{Text- and Token based clone detection}
Clones

\subsection{Big scale clone detection}
There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}

>>>>

%\section{Clone detection survey}
%At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings. Many tools have been proposed to detect various types of code clones. We have considered a set of tools, selected by the most relevant AST or token based detectors found in a set of surveys \cite{}. However, most of these tools have a vastly different purpose than this thesis. Most of the tools are focused on efficiency and detecting all of the types of clones. Efficiency is lesser of a concern to us, correctness is the most important aspect.

%\subsection{Text- and Token based clone detection}
%Most clone detection tools are either text-based or token-based \cite{}. The main rationale for this is that it makes it easy to support many (programming) languages, it is simpler and it is generally more efficient. This works great for most puposes, but for automated refactoring

%\subsection{Big scale clone detection}
%There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}.
